\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{float}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{fancyhdr}

% Modern geometry settings
\geometry{a4paper, margin=1in}

% Modern colors
\definecolor{maincolor}{RGB}{41, 128, 185}
\definecolor{secondcolor}{RGB}{52, 73, 94}
\definecolor{accentcolor}{RGB}{231, 76, 60}

% Modern section formatting
\titleformat{\section}
  {\normalfont\Large\bfseries\color{maincolor}}
  {\thesection}{1em}{}[\titlerule]
  
\titleformat{\subsection}
  {\normalfont\large\bfseries\color{secondcolor}}
  {\thesubsection}{1em}{}

% Modern list formatting
\setlist[itemize]{leftmargin=*,label=\textcolor{maincolor}{$\bullet$}}

% Modern header/footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{secondcolor}{Cat Breed Classification}}
\fancyhead[R]{\textcolor{secondcolor}{\thepage}}
\fancyfoot[C]{\textcolor{secondcolor}{PyTorch Capstone Project}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% Hyperref settings
\hypersetup{
    colorlinks=true,
    linkcolor=maincolor,
    filecolor=maincolor,      
    urlcolor=accentcolor,
    citecolor=maincolor,
}

\title{\textcolor{maincolor}{\Huge PyTorch Capstone Project Report}\\
\textcolor{secondcolor}{\Large Cat Breed Classification System}}
\author{\textcolor{secondcolor}{Wiwat Pholsomboon}}
\date{\textcolor{secondcolor}{April 8, 2025}}

\begin{document}

\maketitle

\section{Introduction}
This project is to study on using PyTorch model to classify cat images. It implements Grad-CAM to visualized the attention of the model on one of CNN layers. ChatGPT-4o-mini is used to identify the image and given the rationale of result. Quiz is implemented to show the accuracy of each model along with human accuracy.

\section{Dataset}
\begin{itemize}
    \item Dataset is from Kaggle from 'Geno Cat Breed Image Collection' dataset (\url{https://www.kaggle.com/datasets/shawngano/gano-cat-breed-image-collection})
    \item Contains 15 cat breeds with 375 photos for each breed (total 5,625 photos)
    \item Preprocessing step
    \begin{itemize}
        \item Resize to 256x256
        \item Random Crop to 224x224
        \item Random Horizontal Flip
        \item Random Rotation
        \item Convert to Tensor
        \item Normalize with mean and std of ImageNet
    \end{itemize}
\end{itemize}

\section{Model Architecture}
\begin{itemize}
    \item Architecture of implemented models:
    \begin{itemize}
        \item 5 Convolutional Layers 
        \item 2 Fully Connected Layers
        \item 1 Dropout Layer in between the two FC Layers
    \end{itemize}
    \item Transfer Learning Models:
    \begin{itemize}
        \item ResNet18 Model (Weights: ImageNet)
        \item EfficientNetB2 Model (Weights: ImageNet)
        \item VGG16 Model (Weights: ImageNet)
    \end{itemize}
\end{itemize}

\section{Training Methodology}
\begin{itemize}
    \item Training process and hyperparameters
    \begin{itemize}
        \item Training Batch Size: 128
        \item Learning Rate: 0.001
        \item Momentum: 0.9
        \item Epochs: 5
        \item Loss Function: Cross Entropy Loss
        \item Optimizer: SGD
    \end{itemize}
\end{itemize}

\section{Results and Evaluation}
\begin{itemize}
    \item Compare Training Accuracy and Loss of each model.
    \item Compare Training Time of each model.
    \item Quiz is implemented to show the accuracy of each model along with human accuracy and ChatGPT-4o-mini accuracy.
\end{itemize}

\section{Visualization and Interpretability}
\begin{itemize}
    \item Implemented Grad-CAM to compared and visualize each model's attention on the image
    \item ChatGPT-4o-mini will give the rationale of its answer.
\end{itemize}

\section{Challenges and Solutions}
\begin{itemize}
    \item Grad-CAM target layer for each model architecture is different and need to be selected manually.
    \item CNN model accuracy is very low, even worse than random guess.
\end{itemize}

\section{Future Improvements}
\begin{itemize}
    \item Apply more data augmentation techniques
\end{itemize}

\section{Conclusion}
\begin{itemize}
    \item Summary of findings
    \item Final model selection and justification
    \item Project outcomes and achievements
\end{itemize}

\end{document}
